---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MlBayesOpt

[![Build Status](https://travis-ci.org/ymattu/MlBayesOpt.svg?branch=master)](https://travis-ci.org/ymattu/MlBayesOpt)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ymattu/MlBayesOpt?branch=master&svg=true)](https://ci.appveyor.com/project/ymattu/MlBayesOpt)
[![Coverage Status](https://img.shields.io/codecov/c/github/ymattu/MlBayesOpt/master.svg)](https://codecov.io/github/ymattu/MlBayesOpt?branch=master)

## Overview
This is an R package to tune hyperparameters for machine learning algorithms
using Bayesian Optimization based on Gaussian Processes. Algorithms currently
supported are: support vector machines, random forest, and xgboost. 

## Dependencies
- rBayesianOptimization
- Matrix
- e1071
- ranger
- xgboost
- dplyr(>= 0.7.0)

## Installation

You can install MlBayesOpt from github with:

```{r gh-installation, eval = FALSE}
# install.packages("githubinstall")
githubinstall::githubinstall("MlBayesOpt")

# install.packages("devtools")
devtools::install_github("ymattu/MlBayesOpt")
```

## Data
### Small Fashion MNIST
`fashion_train` and `fashion_test` are data reproduced from [Fashion-MNIST](https://github.com/zalandoresearch/fashion-mnist). Each data has 1,000 rows and 784 feature column, and 1 label column named `y`.

`fashion` is a data made by the function `bind_rows(fashion_train, fashion_test)`.

### iris
`iris_train` and `iris_test` are included in this pacakge. `iris_train` is odd-numbered rows of `iris` data, and `iris_test`is even-numbered rows of `iris` data.

## Example
```{r load, echo=FALSE, message=FALSE}
devtools::load_all()
```

```{r example}
library(MlBayesOpt)

set.seed(71)
res0 <- svm_opt(train_data = iris_train,
                train_label = Species,
                test_data = iris_test,
                test_label = Species,
                svm_kernel = "sigmoid",
                kappa = 10,
                init_points = 20,
                n_iter = 1)
```

## For Details
See the [vignette](https://ymattu.github.io/MlBayesOpt/articles/MlBayesOpt.html) (Coming Soon!)

## ToDo
- [x] Make functions to execute cross validation
- [ ] Fix minor bugs
