---
title: "MlBayesOpt"
author: "Yuya Matsumura"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R package to tune parameters for machine learning, using bayesian optimization with gaussian process}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = TRUE,
                      comment = "#>",
                      message = FALSE)
```

## Overview
This is an R package to tune hyperparameters for machine learning algorithms using Bayesian Optimization based on Gaussian Processes. Algorithms currently supported are: Support vector machines, Random forest, and XGboost.

This package has some features:

- It's very easy to write Bayesian Optimaization function, but you also able to customise your model very easily.
- Tidy.

### Hyperprameter Tuning in Machine Learning
In many methods of machinelearning, it is very important to tune hyperparameters. "Grid Search" was often used to search the appropriate hyperaprameters, but it takes too much time to compute.


### Machine Learning and Bayesian Optimization in R
We could execute bayesian optimization using `rBayesianOptimization` package in the past.

1. Make the function to maximize
2. Execute the Bayesian Optimization

For example, if we wabt to tune hyperparameters of SVM (Support Vector Machine)


## Installation
You can install **MlBayesOpt** from CRAN:
```{r cran-installation, eval = FALSE}
install.packages("MlbayesOpt")
```

You can install MlBayesOpt (latest dev version) from github with:

```{r gh-installation, eval = FALSE}
# install.packages("githubinstall")
githubinstall::githubinstall("MlBayesOpt")

# install.packages("devtools")
devtools::install_github("ymattu/MlBayesOpt")
```

The source code for **MlBayesOpt** package is available on GitHub at

- https://github.com/ymattu/MlBayesOpt

## Details
### Support Vector Machine


### Random Forest

### XGboost

## Related Works
- [rBayesianOptimization](https://github.com/yanyachen/rBayesianOptimization)
- [e1071](https://cran.r-project.org/web/packages/e1071/index.html)
- [ranger](https://github.com/imbs-hl/ranger)
- [xgboost](https://github.com/dmlc/xgboost)

